Notes on Validated Model Counting \\ Version of \today

### 2022-06-19 doc/mc-notes.tex
Clarification about operator deletion

Finally, operator deletion ({\tt do}) specifies which operator to
delete via the extension variable associated with the operator.  Doing
so for operator $v$ requires 1) there is no (undeleted) operator $u$
having a literal of $v$ as one of its inputs, and 2) there is no
(undeleted) RUP clause containing a literal of $v$.

>>>>

Finally, operator deletion ({\tt do}) specifies which operator to
delete via the extension variable associated with the operator.  Doing
so for operator $v$ requires that there is no
(undeleted) RUP clause containing a literal of $v$.
Implicitly, that means
that there is no (undeleted) operator $u$
having a literal of $v$ as one of its inputs.  The defining clauses for the operation are also deleted.
